Genome Function Phylogenetics

### 2019-04-29 final_project/paper/Paper.Rmd
Updated reproducing section and added reviews

---
title: "Genome Function Phylogenetics"
author: "Dennis Psaroudakis"
date: "April 18th 2019"
keep_md: yes
output:
  tufte::tufte_handout:
    latex_engine: xelatex
    citation_package: natbib
  tufte::tufte_html: default
bibliography: resources/bib.bib
link-citations: yes
classoption: justified
language: en-US
header-includes:
  - \usepackage[osf]{libertine}
  - \citestyle{plain}
---

@@

## Reproducing the Tree
To reproduce this tree, follow these steps on a Linux machine that has PHYLIP available:

```bash
git clone https://github.com/Thyra/EEOB563.git paper_dennis # Clone the repository
cd paper_dennis/final_project # change into the directory
./build_distance_matrix > infile
module load phylip # (if you're on HPC)
neighbor # (use standard options)
```

\noindent The resulting tree is in `outtree`.
Manually root it (e.g. with Dendrogram) outside of the grasses (maize, wheat, barley) and you should end up with the same tree.
This will use the pre-summarized `.tree.json` files in annotation_sets, if you want to completely reproduce it from scratch, delete them and only leave the `.gaf.gz` files.
But be warned, this will take a while to calculate (probably over two hours).

>>>>

---
title: "Genome Function Phylogenetics"
author: "Dennis Psaroudakis"
date: "April 28th 2019"
keep_md: yes
output:
  tufte::tufte_handout:
    latex_engine: xelatex
    citation_package: natbib
  tufte::tufte_html: default
bibliography: resources/bib.bib
link-citations: yes
classoption: justified
language: en-US
header-includes:
  - \usepackage[osf]{libertine}
  - \citestyle{plain}
---

@@

# Reproducing the Tree
To reproduce this tree, follow these steps on a Linux machine that has PHYLIP available:

```bash
git clone https://github.com/Thyra/EEOB563.git paper_dennis # Clone the repository
cd paper_dennis/final_project # change into the directory

# Distance based method
bin/build_distance_matrix annotation_sets/*tree.json > distance_matrix.phy
module load phylip # (if you're on HPC)
neighbor # (use standard options)

# Parsimony based Method
bin/binary_table annotation_sets/*.tree.json > binary.csv
bin/binary2phylip binary.csv > binary.phy
module load phylip
pars # (again, standard options)

# If you're adding more GAFs
bin/gaf2json <new_gaf>
# Then repeat distance or parsimony as above

# To replace GAF filenames with species names in newick tree
bin/rename_taxa <tree.newick> resources/taxa_name_mapping.csv
```

\noindent If any of the binaries fails without a message that says otherwise, you probably need to install some more libraries. If that doesn't help you may have to recompile them for your processor type (they're written in [Crystal](https://crystal-lang.org/), source code is in `src/`)
